Seismic parameter estimation and the Canadian crust

### 2013-03-06 paper/draftBP.tex
prepare for initial manuscript
outline

%% -----------------------------------------------%%
\section{Data and method}
   Seismic data utilized in this study come from 343 stations across Canada from all available networks. Of these stations 146 are of sufficient quality to be useful for study. All stations are broadband with data selected between the years 2000 and 2012, for a total of more than 700 earthquake sources. All teleseismic events outside of the 30 to 100 degrees of epicentral distance are removed before processing. Data is selected for reasonable signal to noise ratio and sufficient impulsiveness that arrival times can be calculated. All data is analyzed using receiver function methods, an approach which has been widely employed over many years to investigate the earths structure.

>>>>

%% -----------------------------------------------%%
\section{Data and method}
    The data utilized in this study are teleseismic P-wave seismograms from 343 broadband stations across Canada. These stations are selected from all available regional and national networks including CNSN, Polaris, FedNor and Chasme. Seismograms have been selected between the years 2000 and 2012 which employ more 1000 earthquake sources. All teleseismic events outside of the 30 to 100 degrees of epicentral distance are removed before processing. Data is selected for reasonable signal to noise ratio and sufficient impulsiveness that arrival times can be calculated. All data is analyzed using receiver function methods, an approach which has been widely employed over many years to investigate the earths structure.
